A comparison of two second order traffic flow models

### 2015-03-13 FirstDraftMaterials/Draft.tex
Added sentence in section 3.2

% PW Model: Hugoniot Loci and Integral Curves
\subsection{Hugoniot Loci and Integral Curves}
In \cite{AwRascle2000}, they consider the simplified PW model
\begin{align*}
&\rho_t + \left( \rho v\right)_x = 0 \\
&\left( \rho v\right)_t + \left( \rho v^2 + p(\rho )\right)_x = 0,
\end{align*}
which is equivalent to the system shown above if we let $1/\tau = 0$ and $\mu = 0$.
From this system, the equation for the Hugoniot loci can be found to be
\begin{align*}
\rho v = \rho v_* \pm \rho \sqrt{\left( \rho - \rho_*\right) \left( p(\rho ) - p(\rho_*)\right) / \rho_*\rho }.
\end{align*}
Using $p(\rho) = \rho^{\gamma}$ for $\gamma \neq 1$, since this is the value used in the AR model we will examine later, the equations for the integral curves can be found to be
\begin{align*}
\rho v = \rho v_* + \frac{2 \rho}{\gamma - 1}\left( \sqrt{p'(\rho_*)} - \sqrt{p'(\rho)}\right)
\end{align*}
for $\lambda_1$, and 
\begin{align*}
\rho v = \rho v_* + \frac{2 \rho}{\gamma - 1}\left( \sqrt{p'(\rho)} - \sqrt{p'(\rho_*)} \right)
\end{align*}
for $\lambda_2$.

>>>>

% PW Model: Hugoniot Loci and Integral Curves
\subsection{Hugoniot Loci and Integral Curves}
In \cite{AwRascle2000}, they consider the homogeneous PW model (arguing that the diffusion term actually makes the model worse, while the relaxation term neither corrects nor adds to the model's problems):
\begin{align*}
&\rho_t + \left( \rho v\right)_x = 0 \\
&\left( \rho v\right)_t + \left( \rho v^2 + p(\rho )\right)_x = 0,
\end{align*}
which is equivalent to the system shown above if we let $1/\tau = 0$ and $\mu = 0$.
From this system, the equation for the Hugoniot loci can be found to be
\begin{align*}
\rho v = \rho v_* \pm \rho \sqrt{\left( \rho - \rho_*\right) \left( p(\rho ) - p(\rho_*)\right) / \rho_*\rho }.
\end{align*}
Using $p(\rho) = \rho^{\gamma}$ for $\gamma \neq 1$, since this is the value used in the AR model we will examine later, the equations for the integral curves can be found to be
\begin{align*}
\rho v = \rho v_* + \frac{2 \rho}{\gamma - 1}\left( \sqrt{p'(\rho_*)} - \sqrt{p'(\rho)}\right)
\end{align*}
for $\lambda_1$, and 
\begin{align*}
\rho v = \rho v_* + \frac{2 \rho}{\gamma - 1}\left( \sqrt{p'(\rho)} - \sqrt{p'(\rho_*)} \right)
\end{align*}
for $\lambda_2$.
